### 2023-07-10 tesis_Ashish/Chapter2/chapter2.tex
update

\item Layer/Disk-Specific Analysis: This type of plot can reveal layer or disk-specific issues. For instance, if one layer's PCC ratio deviates significantly from the norm in high luminosity sections, it might suggest that this layer is particularly sensitive to high luminosity or is underperforming.

>>>>

\item Layer/Disk-Specific Analysis: This type of plot can reveal layer or disk-specific issues. For instance, if one layer's PCC ratio deviates significantly from the norm in high lumi sections, it might suggest that this layer is particularly sensitive to low luminosity or is underperforming.
